Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-12 paper/structureScene.tex
upload table III

\subsubsection*{Role of logarithmic compression}
logarithmic compression provides a small, albeit consistent boost to acoustic scene classification over all folds in the DCASE 2013 private dataset.
Indeed, as discussed in subsection \ref{sec:logcomp}, and observed in Figure \ref{fig:compression}, the statistical assumption of normality for scattering coefficients is only approximately satisfied once mapped to a logarithmic, decibel-like scale.
This transformation improves the discriminative power of support vector machines (SVM) trained on scattering coefficients, whatever be the chosen temporal integration strategy (early or late) or the inner product kernel (linear or Gaussian RBF).
Again, this is in accordance with our previous findings on acoustic scene similarity retrieval, which are reported in Figure \ref{fig:ASS_2}.

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{folds.png}
\caption{Classification accuracies over the five folds of the DCASE 2013 private dataset, for various acoustic descriptors and temporal integration strategies. 
The chosen classifier is a support vector machine (SVM) whose kernel is a Gaussian radial basis function (RBF).
The mean accuracies and fold-wise standard deviations of each experiment are reported in Table \ref{table:dcase2013}.
See text for details}
\end{center}
\ref{fig:folds}
\end{figure}

\begin{table}
\begin{center}
\begin{tabular}{llll}
             & MFCCs         & scattering & log-scattering  \\
             \hline
early, linear  & $54\pm20$   & $62\pm\phantom{0}6$  & $66\pm11$     \\
early, RBF     & $47\pm16$  & $56\pm\phantom{0}7$  & $63\pm\phantom{0}6$   \\
late, linear  & $60\pm\phantom{0}9$ & $70\pm\phantom{0}8$  & $75\pm\phantom{0}5$   \\
late, RBF     & $68\pm10$ & $73\pm\phantom{0}8$  & $\mathbf{78}\pm\phantom{0}6$   \\
\end{tabular}
\caption{Classification accuracies on the DCASE 2013 dataset with various settings of features, temporal integration strategies, and support vector machine kernels.}
\end{center}
\ref{table:dcase2013}
\end{table}

>>>>

\subsubsection*{Role of logarithmic compression}
logarithmic compression provides a small, albeit consistent boost to acoustic scene classification over all folds in the DCASE 2013 private dataset.
Indeed, as discussed in subsection \ref{sec:logcomp}, and observed in Figure \ref{fig:compression}, the statistical assumption of normality for scattering coefficients is only approximately satisfied once mapped to a logarithmic, decibel-like scale.
This transformation improves the discriminative power of support vector machines (SVM) trained on scattering coefficients, whatever be the chosen temporal integration strategy -- \ie early or late -- or the inner product kernel -- \ie linear or Gaussian RBF.
Again, this is in accordance with our previous findings on acoustic scene similarity retrieval, which are reported in Figure \ref{fig:ASS_2}.

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{folds.png}
\caption{Classification accuracies over the five folds of the DCASE 2013 private dataset, for various acoustic descriptors and temporal integration strategies. 
The chosen classifier is a support vector machine (SVM) whose kernel is a Gaussian radial basis function (RBF).
The mean accuracies and fold-wise standard deviations of each experiment are reported in Table \ref{table:dcase2013}.
See text for details.}
\end{center}
\label{fig:folds}
\end{figure}

\begin{table}
\begin{center}
\begin{tabular}{llll}
             & MFCCs         & scattering & log-scattering  \\
             \hline
early, linear  & $54\pm20$   & $62\pm\phantom{0}6$  & $66\pm11$     \\
early, RBF     & $47\pm16$  & $56\pm\phantom{0}7$  & $63\pm\phantom{0}6$   \\
late, linear  & $60\pm\phantom{0}9$ & $70\pm\phantom{0}8$  & $75\pm\phantom{0}5$   \\
late, RBF     & $68\pm10$ & $73\pm\phantom{0}8$  & $\mathbf{78}\pm\phantom{0}6$   \\
\end{tabular}
\caption{Classification accuracies on the DCASE 2013 dataset with various settings of features, temporal integration strategies, and support vector machine kernels.
See text for details.}
\end{center}
\label{table:dcase2013}
\end{table}

@@

\begin{table}
\begin{center}
\begin{tabular}{lcc}
Features & MFCCs & log-scattering \\
Classifier  & GMMs    & linear SVMs \\
Temporal integration & late (product rule) & late (majority voting) \\
\midrule
beach & $74.6 \pm 18.9$ & $83.5 \pm \phantom{0}7.1$ \\
bus & $58.2 \pm 18.3$ & $88.8 \pm 11.4$ \\
caf\'{e} / restaurant & $85.1 \pm 10.8$ & $64.5 \pm \phantom{0}8.3$ \\
car & $69.1 \pm 20.8$ & $94.9 \pm \phantom{0}6.1$ \\
city center & $89.6 \pm \phantom{0}9.2$ & $91.7 \pm \phantom{0}9.4$ \\
forest path & $72.4 \pm 23.8$ & $93.8 \pm \phantom{0}7.8$ \\
grocery store & $74.1 \pm 13.7$ & $90.9 \pm \phantom{0}6.9$ \\
home & $78.1 \pm 17.7$ & $56.2 \pm 23.9$ \\
library & $65.1 \pm 23.3$ & $82.0 \pm 13.0$ \\
metro station & $85.2 \pm 15.6$ & $96.0 \pm \phantom{0}2.3$ \\
office & $90.8 \pm 16.0$ & $87.5 \pm 21.7$ \\
park & $25.6 \pm 11.0$ & $75.4 \pm \phantom{0}7.4$ \\
residential area & $75.1 \pm 19.4$ & $44.2 \pm 15.0$ \\
train & $34.1 \pm \phantom{0}7.2$ & $58.3 \pm 10.0$ \\
tram & $85.4 \pm 13.9$ & $83.7 \pm 12.2$ \\
\bottomrule
Average & $70.8 \pm \phantom{0}2.6$ & $79.4 \pm \phantom{0}3.0$
\end{tabular}
\end{center}
\label{table:dcase2016}
\caption{Class-wise accuracies on the DCASE 2016 dataset for two pipelines: a baseline of mel-frequency cepstral coefficients (MFCCs), Gaussian mixture models (GMMs), and late temporal integration by product of likelihoods ; and our proposed algorithm of log-scattering coefficients, support vector machines (SVMs) with a linear kernel, and late temporal integration by majority voting. See text for details.}
\end{table}
